The next model we consider is an agent-based model. Each individual in the population can be in either of 7 states discussed above: susceptible, exposed, infected, hospitalized, funeral, recovered or dead. The flow between two states is a  probability of transition from one state to another for a typical individual. We represent our model in Figure~\ref{ABM}. In each time step a typical individual who is susceptible to contracting a virus can either transition to exposed state with probability $p_{SE}$ or stay susceptible with probability $p_{SS}$. An individuals in the exposed state transitions to infected with probability $p_{EI}$ and stays exposed with probability $p_{EE}$. An individual who is infected can stay infected, recover, go to a hospital or die and transition to funeral state with probabilities $p_{II},\, p_{IR},\, p_{IH}$ and $p_{IF}$ respectively. Recovery is considered a terminal state so individuals in this state stay in it for the remaining duration of the simulation. Hospitalized individuals may stay hospitalized, transition to recovered or funeral with probabilities $p_{HH}, \, p_{HR}$ and $p_{HF}$. We assume that the individual who dies from Ebola remains infectious through the duration of the entire burial ceremony and no precautions are taken against disease transmission. Safely buried individuals are considered dead and noninfectious and remain in this state for the remaining time of the simulation.  

%  \begin{tikzpicture}[node distance=2cm, font=\tiny]
%        \node [draw, terminal]  (start) at (0,0) {Start};
%        \node [draw, predproc, right of= start] (acquire)(write) {Acquire Image};
%
%%% paths
%    \draw[->](work) -- node[above]{yes}(end);
%    \end{tikzpicture}
\begin{figure}[h!]
\begin{center}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3cm,
  thick,main node/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]

  \node[main node] (1) {S};
  \node[main node] (2) [right of=1] {E};
  \node[main node] (3) [right of=2] {I};
  \node[main node] (4) [right of=3] {R};
    \node[main node] (5) [below left of=3] {D};
      \node[main node] (6) [below right of=3] {F};
        \node[main node] (7) [right of=6] {H};

  \path[every node/.style={font=\sffamily\small}]
    (1)
        edge node {$p_{SE}$} (2)
        edge [loop above] node {$p_{SS}$} (1)
    (2) 
        edge node {$p_{EI}$} (3)
         edge [loop above] node {$p_{EE}$} (2)
      
    (3) 
       edge node {$p_{IR}$} (4)
       edge node[left] {$p_{IF}$} (6)
       edge node {$p_{IH}$} (7)
        edge [loop above] node {$p_{II}$} (3)
    (4)
         edge [loop above] node {$p_{RR}$} (4)
       
(6) edge node{$p_{FD}$} (5) 
edge [loop below] node {$p_{FF}$} (6)     
(7) edge node[right]{$p_{HR}$} (4) 
edge [loop below] node {$p_{HH}$} (7)
  (7) edge node{$p_{HF}$} (6)      
 (5) edge [loop below] node {$p_{DD}$} (5)
        ;
        
\end{tikzpicture}
\end{center}
\caption{Spread of the disease: Agent-based model. Each node represents a typical individual's state. An individual can transition to a state to which he is connected by a directed arc with a probability specified on an arc}
\label{ABM}
\end{figure}
Let

\begin{itemize}
\item[]$t_{IP}$ be the incubation period, i.e. time during which the individual has the virus in his body but does not yet show severe symptoms
\item[] $t_{ID}$ infection duration time after the onset of severe symptoms
\item[] $t_{H}$ time to hospitalization after manifestation of severe symptoms
\item[] $t_{IF}$ time from the onset of severe symptoms to funeral
\item[] $t_{HF}$ time from patient's arrival at the hospital to funeral
\item[] $t_{HR}$ time from patient's arrival at the hospital to recovery
\item[] $t_{DF}$ duration of traditional funeral
\item[] $N$  total number of individuals in a population
\item[] $N_{I}$  total number of individuals in the infected state
\item[] $N_{H}$  total number of individuals in the hospitalized state
\item[] $N_{F}$  total number of individuals in the funeral state
\item[] $\beta_{I}$ rate at which the disease spreads during an interaction with an infected person
\item[] $\beta_{H}$ rate at which the disease spreads during an interaction with a hospitalized person
\item[] $\beta_{F}$ rate at which the disease spreads during an interaction with a person who is in the funeral state
\end{itemize}
We define the individual's probability of transition for each state as

\begin{subequations}
\begin{alignat}{1}
&p_{SE}=\beta_I\cdot \frac{N_{I}}{N}+\beta_H\cdot \frac{N_{H}}{N}+\beta_F\cdot\frac{ N_F}{N}\\
&p_{SS}=1-p_{SE}\\
&p_{EE}=1-\frac{1}{t_{IP}}\\
&p_{EI}=\frac{1}{t_{IP}}\\
&p_{II}=\frac{1}{t_{ID}}\\
&p_{IH}=\frac{1}{t_{H}}\\
&p_{IF}= \frac{1}{t_{IF}}\\
&p_{IR}=1-p_{II}-p_{IH}-p_{IF}\\
&p_{HF}=\frac{1}{t_{HF}}\\
&p_{HR}=\frac{1}{t_{HR}}\\
&p_{HH}=1-p_{HF}-p_{HR}\\
&p_{FF}=\frac{1}{t_{DF}}\\
&p_{FD}=1-p_{FF}\\
&p_{RR}=1\\
&p_{DD}=1
\end{alignat}
\end{subequations}
\subsection{Simulation}We consider a population of size \textbf{100} with \textbf{99} individuals starting in a susceptible state and \textbf{1} individual in the exposed state. Numeric probabilities of an individual transitioning from each state are recorded in Table~\ref{tab:probabilities}. We simulate \textbf{176} days of disease progression without intervention and \textbf{306} days of post intervention disease progression. We repeat the process \textbf{100} times and record the average outcome.  
%
%
% HERE IS THE PROBABILITY TRANSITION TABLE
%
%
%
%
\begin{table}[ht]
\caption{Agent-Model Parameters for Ebola Epidemic in Liberia Before and After the International Intervention} % title of Table
\centering % used for centering table
\begin{tabular}{c c c } 
\hline\hline %inserts double horizontal lines
Parameter & Liberia Before Intervention  & Liberia After Intervention \\ [0.5ex] 
 & (Mar/14 to Sept/14) &  (Sept/14 to Jul/15) \\ [0.5ex] % inserts table
% inserts table
%heading
\hline % inserts single horizontal line
$p_{SE}$ & \textbf{DYNAMIC} & \textbf{DYNAMIC} \\ 
$p_{SS}$ & \textbf{COMPUTE}8 & \textbf{COMPUTE}  \\ 
$p_{EE}$ & 0.9091 & 0.9091  \\ 
$p_{EI}$ & 0.0909 & 0.0909  \\ 
$p_{II}$ & 0.1 & 0.1  \\ 
$p_{IH}$ & 0.2227 & 0.2160  \\ 
$p_{IF}$ & 0.125 & 0.125  \\ 
$p_{IR}$ & 0.5523 & 0.559  \\ 
$p_{HF}$ & 0.2849 & 0.2849 \\ 
$p_{HR}$ & 0.1815 & 0.1815 \\ 
$p_{HH}$ & 0.5336& 0.5336  \\ 
$p_{FF}$ & 0.5 & 0.5 \\ 
$p_{FD}$ & 0.5 & 0.5  \\ 
$p_{RR}$ & 1 & 1  \\ 
$p_{DD}$ & 1 & 1 \\ [1ex] 
\hline 
\end{tabular}
\label{tab:probabilities}
\end{table}
%
%
%
%
%
