In this paper we examined time series data of the number of Ebola cases and deaths in Liberia during the 2014-2015 outbreak. Through a system dynamics approach, we showed that intervention can have a significant impact on the spread of the disease. A change in model parameters, caused by international intervention, decreased Ebola's reproductive number from 1.99 to 0.787. Because system dynamics is a deterministic approach, we also looked at an agent-based variation of the model, which allows us to observe realizations with and without outbreaks (if the infected individual dies, the disease is not spread). Through different realizations, we saw that in 70\% of the instances Ebola would spread to more than 2\% of the population with severe consequences: half of the population dies. Through the probabilistic model we also studied the effect of intervention. If the intervention is started early, when only 1\% of the population is exposed to the disease, only 2\% of the population dies. This model assumed that the population is well-mixed, which is unrealistic -- for example, in Africa there are many small villages and larger cities, and the spread of a disease can depend highly on the amount of movement of the infected individuals. The recent Ebola outbreak started in one such small village. To take such inhomogeneous densities into account, we then incorporated spatial movement into an agent-based model and allowed for different types of individuals (family vs. community) and local transmission of the infection. In this setting, the outbreaks can be less severe due to the environment not being well-mixed. When tracking how many infections result from different types of contact, the spread between community members accounts for the highest proportion of transmission. The transmission during funerals is still significant, however, and reducing the common practices of touching the deceased at a funeral would lower the number of infected individuals. 

The system dynamics approach provides the average expected dynamics of an Ebola outbreak and clearly shows the parameter's effects to the model in the system of differential equations. The non-spatial agent-based model gives a probabilistic approach to such average dynamics, allowing Ebola cases to die out and prevent outbreaks. This model is appropriate to use in a well-mixed population. In a population that is not well-mixed or with multiple cities and villages that are spatially disconnected, the spatial agent-based model provides a more flexible model although the parameters interactions are less clear than in the previous two models.

There are several factors one may wish to take into account when analyzing how a virus spreads in a community. We took into account characteristics of the virus itself: incubation period, the rate of recovery, mortality rate and society's cultural perspective on a proper burial ceremony. In the spatial model we also attempted to incorporate frequency and nature of individuals' interactions, and distance and frequency of travel to other villages. Other factors also play a role in the spread of the disease. Having information about the local government and the wealth of the region would help to determine the capacity of response when facing an epidemic, including the quantity and quality of hospitals, their capacity, and the number of health-care professionals as well as their level of expertise. In the moment of a virus outbreak, governments from other countries may intervene to help to control the disease, possibly decreasing the number of infected people and increasing the number of recovered patients, by educating individuals about the virus and its mode of transmission as well as properly handling the deceased family. One realization of the result of such action we saw during 2014-2015 Ebola outbreak in Liberia. Such social parameters could be incorporated into our models.